### 2021-10-22 article.tex
Import TLPwMT

\FMSyntaxEvaluation{\SystemFm syntax and evaluation rules for a given set of classes $\C$ with class inheritance $\Ψ$ \\and class disjointness $\Ξ$. \hl{\text{Highlights}} correspond to additions to \SystemFsub.}

@@

\subsection{Shape Errors in Python}
In the example Python code below, the \python{img_batch} ndarray is a batch of 25 randomly generated RGB images of size 256$\×$256.
The code aims to compute a vector of length 25 containing the average grayscale color of each image in the batch, and then create a square 5$\×$5 image of the average grayscale colors.
However, this code contains a shape error and will throw an error at runtime.
%
\badreducecodesection
%
The error is in the call to \python{np.mean}, which takes as argument a list of axes to reduce along.
Unfortunately, the arguments to \python{np.mean} are off-by-one and result in a vector of length 3 (\python{img_batch}'s last dimension) instead of the intended length of 25 (\python{img_batch}'s first dimension); \python{avg_color} thus contains the average RGB color of the batch instead of the average grayscale color for each image.
The reshape operation will then fail at runtime, as it cannot reshape a 3-element vector into a 25-element matrix.
This error can be difficult to spot, given that NumPy's interface for reducing along multiple axes is index-based.
Runtime errors like this one can be particularly frustrating when they occur late in a long-running computation.

>>>>

\FMSyntaxEvaluation{\SystemFm syntax and evaluation rules for a given set of classes $\C$ with class inheritance $\Ψ$ and class disjointness $\Ξ$. \hl{\text{Highlights}} correspond to additions to \SystemFsub.}

@@

\subsection{Shape Errors in Python}
In the example Python code below, the \python{img_batch} ndarray is a batch of 25 randomly generated RGB images of size 256$\×$256.
The code aims to compute a vector of length 25 containing the average grayscale color of each image in the batch, and then create a square 5$\×$5 image of the average grayscale colors.
However, this code contains a shape error and will throw an error at runtime.
%
\begin{lstlisting}[style=py]
import numpy as np
img_batch = np.random.normal(size=(25, 256, 256, 3))
avg_colors = np.mean(img_batch, (0, 1, 2))
avg_color_square = np.reshape(avg_colors, (5, 5))
\end{lstlisting}
%
The error is in the call to \python{np.mean}, which takes as argument a list of axes to reduce along.
Unfortunately, the arguments to \python{np.mean} are off-by-one and result in a vector of length 3 (\python{img_batch}'s last dimension) instead of the intended length of 25 (\python{img_batch}'s first dimension); \python{avg_color} thus contains the average RGB color of the batch instead of the average grayscale color for each image.
The reshape operation will then fail at runtime, as it cannot reshape a 3-element vector into a 25-element matrix.
This error can be difficult to spot, given that NumPy's interface for reducing along multiple axes is index-based.
Runtime errors like this one can be particularly frustrating when they occur late in a long-running computation.
